### 2018-11-12 source/Ch2-techniques/imaging.tex
added neal comments
asdasda

\pg
There are two quantities of interest to all astronomers: sensitivity and angular resolution\footnote{Other kinds of resolution - in time and frequency, for example - are also extremely important to many astronomers, but are not what concern us here.}. An instrument's sensitivity is a function of its collecting area\footnote{It is also a function of technological factors, of course, but \emph{ceteris paribus}, a more sensitive telescope means a telescope with a wider collecting area}. Resolution, for well-designed instruments\footnote{By this, we mean that we assume that an instrument is also designed to optimise resolution.}, is limited by diffraction in the absence of atmospheric effects. This introduces specific issues in the radio domain. Radio waves have very long wavelengths - often comparable to meters, rather than the $\sim100-1000$nm wavelengths of optical light. Achieving a resolution comparable to those of optical telescopes would thus require making telescopes with apertures tens of millions of times larger than those already titanic instruments!

@@

\pg
To define the baseline, we must begin by considering the geometric properties of an interferometric array. For now, let us assume that we are observing the sky above the array, a practice known as drift-scanning. A baseline then consists of the vector subtraction of the positions, in 3-dimensional space, of its two constituent antennas. Note that each antenna pair therefore has 2 corresponding baselines, since for each pair of antennas A and B we create baselines AB and BA. These distance vectors are then divided by the observing wavelength to give a dimensionless set of coordinates, known as $(u,v,w)$. These coordinates define the baseline entirely.

@@

\pg
We have defined what a baseline corresponds to: a vector coordinate in $(u,v,w)$-space. To each baseline we associate a measurement, which we call the \emph{visibility}. 
\begin{figure}[ht]
\centering
\includegraphics[width=.7\textwidth]{images/visibility-creation.png}
\caption{\label{fig.visibility} There are two ways to combine the voltages from two antennas into a visibility: they are sum-correlation and $\pi$-correlation. In this manuscript, we will only concern ourselves with the latter. Image credit: Julien Girard}
\end{figure}
The visibility associated with baseline $\mathbf{b}_{AB}$ is created by taking the voltage $V_A$ measured by antenna A, multiply it by the complex conjugate $V_B^*$ of the voltage measured by antenna B, average over the correlator dump time (i.e. the time over which the measurement is made). This scalar quantity is associated to the baseline position vector $\mathbf{b}_{AB}$. In other words:
\begin{align}
\mathbf{b}_{AB} &= \frac{\mathbf{x}_{B}-\mathbf{x}_{A}}{\lambda_\mathrm{obs}}\\
V_{AB}          &= \langle V_{A} V_{B}^*\rangle_{\delta t, \delta \nu} 
\end{align}
where $\langle \cdots \rangle_{i}$ denotes an averaging over quantity $i$. We see that a visibility is a complex vector quantity. We also see that $\mathbf{b}_{AB} = \mathbf{b}_{BA}^*$: the information of the visibility associated with baseline BA is contained in the visibility associated with baseline AB. This means that in practice, only half of the visibilities ever need be stored. What does the visibility measurement correspond to?
\begin{figure}[ht]
\centering
\includegraphics[width=.5\textwidth]{images/visibility-measure.png}
\caption{\label{fig.visibility.measure} Here, we assume that there are only two sources in the sky whose signal can be measured by our antennas. The final visibility is the sum of the visibilities associated with each individual source. Image credit: Julien Girard \citepads{julien}}
\end{figure}

\pg
The signals from different astrophysical do not interfere. They are measured additively in both antennas. Provided that the signal from each sources is coherent when observed by the dishes, the correlation between the voltages measured by antennas A and B will simply be the sum of the voltage correlations associated with individual sources. This is shown in \cref{fig.visibility}: the radio signal from two different sources, at two different locations, is picked up simultaneously by both radio antennas. Because only the correlation between both antennas is measured, the signals do not interfere: if the signal from each source gives a voltage $V_{p}^s$ for antenna $p$, then the additive property of electric fields means that the total visibility measured by baseline $pq$ can be written as:
\begin{align}
V_{pq}  &= \langle \left(\sum_{s} V_{p}^s\right) \left(\sum_{s} (V_{q}^s)\right)^*  \rangle_{\Delta t} \\
        &= \langle \sum_{s,s'} V_{p}^s (V_q^{s'})^*  \rangle_{\Delta t}\\
        &= \langle \sum_s V_{p}^s (V_q^{s})^* \rangle_{\Delta t} + \underbrace{\langle \sum_{s,s'\ne s} V_{p}^s (V_q^{s'})^* \rangle_{\Delta t}}_{=0} \label{eq.spatial.incor}
\end{align}
where the fact that signal from different sources is not coherent means that we average out cross-contributions (i.e. signal from $s\ne s'$). 
%\begin{align}
%V_{pq}&=\langle \left(\sum_{s} V_{p}^s\right) \left(\sum_{s} V_{q}^s \right)^* \rangle_{\Delta t} \right)\\
%      &=\langle\sum_{s,s'} \left( V_p^s\left(V_q^{s'}\right)^* \rangle_{\Delta t}
%\end{align}

\pg
Note that in Fig. \ref{fig.visibility.measure}, neither source is at the zenith. This introduces the notion of the \emph{effective baseline} which is shorter than the \emph{physical baseline} when measuring a signal from a source that is not at the zenith. Sources in different positions in the sky will be measured by an interferometric array, but the same array will have different effective baselines for different sources. To point an interferometric array in a specific direction in the sky, one must introduce a phase delay in each antenna (or, for fundamental interferometer elements such as the LOFAR tiles or NenuFAR, by playing with the cable length between each dish and the correlator). This is done by three means: delay tracking (which is exact only for the delay tracking centre\footnote{Source: \url{http://www.astron.nl/eris2013/Documents/2_laing_fundamentals_interferometry.pdf}, \url{https://science.nrao.edu/science/meetings/2016/15th-synthesis-imaging-workshop/SISS15Advanced.pdf}}, and corresponds to playing with the cable length between antennas in the interferometric array), antenna pointing\footnote{This maximises antenna sensitivity in a given direction, but is not done with LOFAR}, and fringe stopping\footnote{Fringe stopping consists of down-converting the signal received by antennas by mixing with a local oscillator. The geometric delay compensation is usually applied on this down-converted signal. Source: \url{http://www.gmrt.ncra.tifr.res.in/gmrt_hpage/Users/doc/WEBLF/LFRA/node74.html}}.
%Fringe stopping consists of measuring the beat between a predicted fringe rate (i.e. the period of the visibility sine wave corresponding to a point source out of phase centre; if the position of an array's antennas is well-known, this can be modeled accurately) and a known signal, e.g. the actual fringe rate (i.e. the fringe rate corresponding to the true period of the visibility sine wave). The difference between the two is a function of how well the antennas' positions are known. If they are well-known, then the phase information can still be measured, even without very fine sampling in time. } must be used to avoid taking a measurement every few milliseconds. 
This means that there are actually three different ``field centres", which are usually (but not always) set to be the same: the pointing (direction of maximum antenna sensitivity), the delay (which can be introduced in cable length) and the phase tracking (which consists of applying a known signal to the measured signal and recording the resulting heterodyne wave so as to keep a reasonable amount of post-correlation data without losing information on sources outside of the phase delay centre). The position of sources are then given in terms of the cardinal angle $\sigma$: this is the difference between the position of a source and the phase centre, which is where the array is pointing. For example, in \cref{fig.visibility.measure}, if we point antennas and introduce phase delays such that we are pointing the array towards Source 2, the position of Source 1 will be $\sigma$.

@@

\pg
Individual antennas of an array can be pointed mechanically, and so the loss of antenna sensitivity in the direction of interest (and therefore the loss of net interferometric array sensitivity) can be minimised. But what happens to the array itself? It is useful here to go back to the illustration of Fig. \ref{fig.arecibo.vla}. Think of each dish in the array representing a "filled" segment of a massive but empty dish. By projecting our observation in a given direction, this dish goes from circular to elliptical.
\begin{figure}[ht]
\centering
\begin{subfigure}{.40\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/lofar-uvcoverage-zenith.png}}
\caption{\label{fig.lofar.uvcoverage.zenith} $uv$-coverage of an 8-hour LOFAR observation when pointing at zenith.}
\end{subfigure}
\hfill
\begin{subfigure}{.40\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/lofar-uvcoverage-elsewhere.png}}
\caption{\label{fig.lofar.uvcoverage.elsewhere} $uv$-coverage of an 8-hour LOFAR observation when pointing 45 degrees away from zenith.}
\end{subfigure}
\caption{\label{fig.uvcoverage.lofar} Effect of array pointing on $uv$-coverage. By pointing the array 45 degrees in the $v$-axis, the array's $uv$-coverage (and thus maximum resolution) is decreased along the $v$-axis. Two colours are used, because $V_{AB}=V_{BA}$, and so only half the visibilities are stored in practice.}
\end{figure}

@@

\pg
We have seen that the purpose an interferometric array is to overcome the diffraction limit of single-dish antennas. We have described visibilities, which are the quantities measured by an interferometric array. What remains is to describe how these measurements are related to the sky brightness distribution.

\pg
Assuming that all the antennas in an array are equivalent and perfectly calibrated, the van Cittert-Zernike theorem (\citetads{1934Phy.....1..201V}, covered in \citetads{2001isra.book.....T}) allows us to equate a visibility with a single Fourier mode of the plane tangent to the sky where the instrument is pointed. This direction is called the \emph{phase centre}, because phase shifts are introduced between antenna voltages before averaging so as to point each visibility in this direction. This behaviour is encoded in the Fourier kernel, which is written as:
\begin{equation}
k_p=2\pi i (( u_p l + v_p m + w_p (n-1) ))
\end{equation}

\pg
The Point-Spread Function (PSF) of an instrument is its point source response: it will determine the angular resolution limit due to the instrument. We know that the Fourier transform of a single point source with unit flux at phase centre is a constant. If we measured the full (infinite) visibility space, then we could reconstitute a point source perfectly. In practice, however, we only ever measure a subset of the visibility space: an interferometric array's PSF is thus the inverse Fourier transform of the array's $uv$-coverage, as these are the only points for which we have information on visibility space. The more elements in the array, the better the $uv$-coverage and thus the better the PSF. An interferometer's PSF will always be worse than an antenna dish of equivalent diameter, the UV-coverage of which is the inverse Fourier transform of a disc. This is because an interferometer behaves like a \emph{sparse} dish: the sparsity of our coverage manifests as very large point-spread function. The more baselines are available, the less sparse the UV-coverage, and so the better the PSF. This is shown in Fig. \ref{fig.vla.PSFvsUVcov}.

\pg
Mathematically, the $uv$-coverage of an interferometer can be treated as a series of delta functions centred on the antenna positions. To go from visibility space to image space, we apply the inverse Fourier transform, giving us:
\begin{align}
\mathbf{S}_{\mathrm{obs}} &= \mathcal{F}^*\left[ \mathbf{B} \sum_i^{n} \mathbf{x}_i \right]
\end{align}
where $\mathbf{S}_{\mathrm{obs}}$ is the observed sky brightness distribution, $\mathbf{B}$ the Fourier transform of the true sky brightness distribution $\mathbf{S}$, and $n$ is the number of antennas in our array. $\mathcal{F}^*$ is the inverse Fourier transform. By using the convolution theorem, we immediately see that
\begin{align}
\mathbf{S}_{\mathrm{obs}} &= \underbrace{\mathcal{F}^*\left[ \mathbf{B}\right]}_{=\mathbf{S}} \star \underbrace{\mathcal{F}^*\left[\sum_i^{n}\mathbf{x}_i \right]}_{\text{the PSF}}\\
\end{align}
and that our image is the convolution of the ``true", underlying sky brightness distribution, and our array's PSF. As $n \rightarrow \infty$, the $uv$-plane fills, and the inverse Fourier transform of this unit plane becomes 1. This illustrates the description above.

@@

\pg
Bad conditioning and non-convexity can be alleviated through regularisation: by specifying a well-chosen prior (e.g. for interferometry, using a good sky model for calibration), the underlying distribution of the solutions can be constrained to fall in a narrow, convex region. This is shown in \cref{fig.selfcal.regularise}
\begin{figure}[h!]
	\includegraphics[width=.6\linewidth]{images/regularise.png}
	\caption{\label{fig.selfcal.regularise} Plot showing the effect of regularisation on an ill-conditioned, non-convex problem. The $\chi^2$ fit is constrained to lie in a convex, well-conditioned region: it falls within the global minimum, at at one point only rather than somewhere in a valley.}
\end{figure}

@@

\pg
We close this section by noting that data flagging can be considered a form of weighting scheme. This consists of assigning a null weight to those data points considered too corrupted by various instrumental or atmospheric effects (typically, Radio Frequency Interference - RFI - cf. \citetads[cf.]{2010ascl.soft10017O} for an example) to be scientifically useful. Those weights which are not deemed too corrupted are assigned a weight of zero. This corresponds to simply dropping those data points which would corrupt the image reconstruction by introducing unphysically strong fringes in the image.

@@

\pg
So far, the astronomer will have worked entirely with visibilities. However, generally speaking, the aim will be to get information on the object's spatial brightness distribution at the observing frequency. This will require \emph{imaging}: going from visibilities to the image-plane. This can be done through a variety of tools, but will generally involve deconvolution. Imaging will be the subject of the rest of this chapter, and deconvolution will be described in more detail in \cref{section.clean}.

\pg
After obtaining the initial image, it may be desirable to perform a few rounds of self-calibration \citepads[cf.]{2018arXiv180505266B} on the target field. This consists of extracting a model from the initial image and using it as a new calibration model, then re-imaging. Doing this will usually dramatically improve the final image.

\pg
The framework for interferometric calibration is complex, and understanding it requires a good grasp on interferometry itself. For now, we will assume that calibration has been performed perfectly, and that the gain-corrections have been applied to the voltage measured by our antennas. We therefore work with the true signal from astrophysical sources until \cref{section.RIME}.

>>>>

\pg
There are two quantities of interest to all astronomers: sensitivity and angular resolution\footnote{Other kinds of resolution - in time and frequency, for example - are also extremely important to many astronomers, but are not what concern us here.}. An instrument's sensitivity is a function of its collecting area\footnote{It is also a function of technological factors, of course, but \emph{ceteris paribus}, a more sensitive telescope means a telescope with a wider collecting area}. Resolution, for well-designed instruments\footnote{By this, we mean that we assume that an instrument is also designed to optimise resolution.}, is limited by diffraction in the absence of atmospheric effects. This introduces specific issues in the radio domain. Radio waves have very long wavelengths - often comparable to meters, rather than the $\sim100-1000$nm wavelengths of optical light. Achieving a resolution comparable to that of optical telescopes would thus require making telescopes with apertures tens of millions of times larger than those already titanic instruments!

@@

\pg
To define the baseline, we must begin by considering the geometric properties of an interferometric array. For now, let us assume that we are observing the sky above the array, a practice known as drift-scanning. A baseline then consists of the vector subtraction of the positions, in 3-dimensional space, of its two constituent antennas. Note that each antenna pair therefore has 2 corresponding baselines, since for each pair of antennas A and B we create baselines AB and BA. These distance vectors are then divided by the observing wavelength to give a dimensionless set of Cartesian coordinates, known as $(u,v,w)$. These coordinates define the baseline entirely.

@@

\pg
We have defined what a baseline corresponds to: a vector coordinate in $(u,v,w)$-space. To each baseline we associate a measurement, which we call the \emph{visibility}. 
\begin{figure}[ht]
\centering
\includegraphics[width=.7\textwidth]{images/visibility-creation.png}
\caption{\label{fig.visibility} There are two ways to combine the voltages from two antennas into a visibility: they are sum-correlation and $\pi$-correlation. In this manuscript, we will only concern ourselves with the latter. Image credit: Julien Girard}
\end{figure}
The visibility associated with baseline $\mathbf{b}_{AB}$ is created by taking the voltage $V_A$ measured by antenna A, multiply it by the complex conjugate $V_B^*$ of the voltage measured by antenna B, averaged over the correlator dump time (i.e. the time over which the measurement is made). This is shown on the right-hand side of \cref{fig.visibility}. This scalar quantity is associated to the baseline position vector $\mathbf{b}_{AB}$, given by the difference in the Cartesian positions of the antennas $\mathbf{x}_{A}$ and $\mathbf{x}_{B}$. In other words:
\begin{align}
\mathbf{b}_{AB} &= \frac{\mathbf{x}_{B}-\mathbf{x}_{A}}{\lambda_\mathrm{obs}}\\
V_{AB}          &= \langle V_{A} V_{B}^*\rangle_{\Delta t, \Delta \nu} 
\end{align}
where $\langle \cdots \rangle_{i}$ denotes an averaging over quantity $i$. We see that a visibility is a complex vector quantity. We also see that $\mathbf{b}_{AB} = \mathbf{b}_{BA}^*$: the information of the visibility associated with baseline BA is contained in the visibility associated with baseline AB. This means that in practice, only half of the visibilities ever need be stored. What does the visibility measurement correspond to?
\begin{figure}[ht]
\centering
\includegraphics[width=.5\textwidth]{images/visibility-measure.png}
\caption{\label{fig.visibility.measure} Here, we assume that there are only two sources in the sky whose signal can be measured by our antennas. The final visibility is the sum of the visibilities associated with each individual source. Image credit: Julien Girard \citepads{julien}}
\end{figure}

\pg
The signals from different astrophysical sources do not interfere. They are measured additively in both antennas. Provided that the signal from each source is coherent when observed by the dishes, the correlation between the voltages measured by antennas A and B will simply be the sum of the voltage correlations associated with individual sources. This is shown in \cref{fig.visibility.measure}: the radio signal from two different sources, at two different locations, is picked up simultaneously by both radio antennas. Because only the correlation between both antennas is measured, the signals do not interfere: if the signal from each source gives a voltage $V_{p}^s$ for antenna $p$, then the additive property of electric fields means that the total visibility measured by baseline $pq$ can be written as:
\begin{align}
V_{pq}  &= \langle \left(\sum_{s} V_{p}^s\right) \left(\sum_{s} (V_{q}^s)\right)^*  \rangle_{\Delta t} \\
        &= \langle \sum_{s,s'} V_{p}^s (V_q^{s'})^*  \rangle_{\Delta t}\\
        &= \langle \sum_s V_{p}^s (V_q^{s})^* \rangle_{\Delta t} + \underbrace{\langle \sum_{s,s'\ne s} V_{p}^s (V_q^{s'})^* \rangle_{\Delta t}}_{=0} \label{eq.spatial.incor}
\end{align}
where the fact that signal from different sources $s$ and $s'$ (i.e. where $s\ne s'$) is not coherent means that we average out cross-contributions. 
%\begin{align}
%V_{pq}&=\langle \left(\sum_{s} V_{p}^s\right) \left(\sum_{s} V_{q}^s \right)^* \rangle_{\Delta t} \right)\\
%      &=\langle\sum_{s,s'} \left( V_p^s\left(V_q^{s'}\right)^* \rangle_{\Delta t}
%\end{align}

\pg
Note that in Fig. \ref{fig.visibility.measure}, neither source is at the zenith. This introduces the notion of the \emph{effective baseline} which is shorter than the \emph{physical baseline} when measuring a signal from a source that is not at the zenith. Sources in different positions in the sky will be measured by an interferometric array, but the same array will have different effective baselines for different sources. To point an interferometric array in a specific direction in the sky, one must introduce a phase delay in each antenna (or, for fundamental interferometer elements such as the LOFAR tiles or NenuFAR, by playing with the cable length between each dish and the correlator). This is done by three means: delay tracking (which is exact only for the delay tracking centre\footnote{Source: \url{http://www.astron.nl/eris2013/Documents/2_laing_fundamentals_interferometry.pdf}, \url{https://science.nrao.edu/science/meetings/2016/15th-synthesis-imaging-workshop/SISS15Advanced.pdf}}, and corresponds to playing with the cable length between antennas in the interferometric array), antenna pointing\footnote{This maximises antenna sensitivity in a given direction, but is not done with LOFAR}, and fringe stopping\footnote{Fringe stopping consists of down-converting the signal received by antennas by mixing with a local oscillator. The geometric delay compensation is usually applied on this down-converted signal. Source: \url{http://www.gmrt.ncra.tifr.res.in/gmrt_hpage/Users/doc/WEBLF/LFRA/node74.html}}.
%Fringe stopping consists of measuring the beat between a predicted fringe rate (i.e. the period of the visibility sine wave corresponding to a point source out of phase centre; if the position of an array's antennas is well-known, this can be modeled accurately) and a known signal, e.g. the actual fringe rate (i.e. the fringe rate corresponding to the true period of the visibility sine wave). The difference between the two is a function of how well the antennas' positions are known. If they are well-known, then the phase information can still be measured, even without very fine sampling in time. } must be used to avoid taking a measurement every few milliseconds. 
This means that there are actually three different ``field centres", which are usually (but not always) set to be the same: the pointing (direction of maximum antenna sensitivity), the delay (which can be introduced in cable length) and the phase tracking (which consists of applying a known signal to the measured signal and recording the resulting heterodyne wave so as to keep a reasonable amount of post-correlation data without losing information on sources outside of the phase delay centre). The position of sources are then given in terms of the cardinal\footnote{So-called because, in the case where these angles are small, they correspond to positions along the cardinal directions.} angle $\sigma$: this is the difference between the position of a source and the phase centre, which is where the array is pointing. For example, in \cref{fig.visibility.measure}, if we point antennas and introduce phase delays such that we are pointing the array towards Source 2, the position of Source 1 will be $\sigma$.

@@

\pg
Individual antennas of an array can be pointed mechanically, and so the loss of antenna sensitivity in the direction of interest (and therefore the loss of net interferometric array sensitivity) can be minimised. But what happens to the array itself? It is useful here to go back to the illustration of Fig. \ref{fig.arecibo.vla}. Think of each dish in the array representing a ``filled" segment of a massive but empty dish. By pointing our observation in a given direction, this dish is transformed - the absolute positions of the ``filled" segments remain constant, and so their relative position after transformation is changed. Our ``sparse dish" goes from circular to elliptical. This is shown in \cref{fig.uvcoverage.lofar}.
\begin{figure}[ht]
\centering
\begin{subfigure}{.40\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/lofar-uvcoverage-zenith.png}}
\caption{\label{fig.lofar.uvcoverage.zenith} $uv$-coverage of an 8-hour LOFAR observation when pointing at zenith.}
\end{subfigure}
\hfill
\begin{subfigure}{.40\textwidth}
\resizebox{\hsize}{!}{\includegraphics{images/lofar-uvcoverage-elsewhere.png}}
\caption{\label{fig.lofar.uvcoverage.elsewhere} $uv$-coverage of an 8-hour LOFAR observation when pointing 45 degrees away from zenith.}
\end{subfigure}
\caption{\label{fig.uvcoverage.lofar} Effect of array pointing on $uv$-coverage. By pointing the array 45 degrees in the $v$-axis, the array's $uv$-coverage (and thus maximum resolution) is decreased along the $v$-axis. Two colours are used, because $V_{AB}=V_{BA}$, and so only half the visibilities are stored in practice.}
\end{figure}

@@

\pg
We have seen that the purpose of an interferometric array is to overcome the diffraction limit of single-dish antennas. We have described visibilities, which are the quantities measured by an interferometric array. What remains is to describe how these measurements are related to the sky brightness distribution.

\pg
Assuming that all the antennas in an array are equivalent and perfectly calibrated, the van Cittert-Zernike theorem (\citetads{1934Phy.....1..201V}, covered in \citetads{2001isra.book.....T}) allows us to equate a visibility with a single Fourier mode of the plane tangent to the sky where the instrument is pointed. This direction is called the \emph{phase centre}, because phase shifts are introduced between antenna voltages before averaging so as to point each visibility in this direction. This behaviour is encoded in the Fourier kernel, which is written as:
\begin{equation}
k_p=2\pi i (( u_p l + v_p m + w_p (n-1) ))
\end{equation}
where $k_p$ is the Fourier kernel for antenna $p$, $(l,m,n)$ are cardinal sine directions, and $(u_p,v_p,w_p)$ are the $uvw$-coordinates of antenna p.

\pg
The Point-Spread Function (PSF) of an instrument is its point source response: it will determine the angular resolution limit due to the instrument. We know that the Fourier transform of a single point source with unit flux at phase centre is a constant. If we measured the full (infinite) visibility space, then we could reconstitute a point source perfectly. In practice, however, we only ever measure a subset of the visibility space: an interferometric array's PSF is thus the inverse Fourier transform of the array's $uv$-coverage, as these are the only points for which we have information on visibility space. An interferometer's PSF will always be worse than an antenna dish of equivalent diameter, the UV-coverage of which is the inverse Fourier transform of a disc. This is because an interferometer behaves like a \emph{sparse} dish: the sparsity of our coverage manifests as very large point-spread function. The more elements in the array, the better the $uv$-coverage (as more baselines are available), the less sparse the UV-coverage, and so the better the PSF. This is shown in Fig. \ref{fig.vla.PSFvsUVcov}.

\pg
Mathematically, the $uv$-coverage of an interferometer can be treated as a series of delta functions centred on the antenna positions. To go from visibility space to image space, we apply the inverse Fourier transform, giving us:
\begin{align}
\mathbf{S}_{\mathrm{obs}} &= \mathcal{F}^*\left[ \mathbf{B} \sum_i^{n} \mathbf{x}_i \right]
\end{align}
where $\mathbf{S}_{\mathrm{obs}}$ is the observed sky brightness distribution, $\mathbf{B}$ the Fourier transform of the true sky brightness distribution $\mathbf{S}$, $\mathbf{x}_i$ is the Dirac delta function centred on the position of antenna $i$, and $n$ is the number of antennas in our array. $\mathcal{F}^*$ is the inverse Fourier transform. By using the convolution theorem, we immediately see that
\begin{align}
\mathbf{S}_{\mathrm{obs}} &= \underbrace{\mathcal{F}^*\left[ \mathbf{B}\right]}_{=\mathbf{S}} \star \underbrace{\mathcal{F}^*\left[\sum_i^{n}\mathbf{x}_i \right]}_{\text{the PSF}}\\
\end{align}
and that our image is the convolution of the ``true", underlying sky brightness distribution, and our array's PSF. As $n \rightarrow \infty$, the $uv$-plane fills, and the inverse Fourier transform of this unit plane becomes 1. This illustrates the description above.

@@

\pg
Bad conditioning and non-convexity can be alleviated through regularisation: by specifying a well-chosen prior (e.g. for interferometry, using a good sky model for calibration), the underlying distribution of the solutions can be constrained to fall in a narrow, convex region. This is shown in \cref{fig.selfcal.regularise}
\begin{figure}[h!]
	\includegraphics[width=.6\linewidth]{images/regularise.png}
	\caption{\label{fig.selfcal.regularise} Plot showing the effect of regularisation on an ill-conditioned, non-convex problem. The $\chi^2$ fit is constrained to lie in a convex, well-conditioned region: it falls within the global minimum, at one point only rather than somewhere in a valley.}
\end{figure}

@@

\pg
We close this section by noting that data flagging can be considered a form of weighting scheme. This consists of assigning a null weight to those data points considered too corrupted by various instrumental or atmospheric effects (typically, Radio Frequency Interference - RFI - cf. \citetads[cf.]{2010ascl.soft10017O} for an example) to be scientifically useful. Those weights which are deemed too corrupted are assigned a weight of zero. This corresponds to simply dropping those data points which would corrupt the image reconstruction by introducing unphysically strong fringes in the image.

@@

\pg
So far, the astronomer will have worked entirely with visibilities. However, generally speaking, the aim will be to get information on the object's spatial brightness distribution at the observing frequency. This will require \emph{imaging}: going from visibilities to the image-plane. This can be done through a variety of tools, but will generally involve deconvolution. All that was covered so far was imaging: specific examples of deconvolution itself were given in \cref{section.clean}.

\pg
After obtaining the initial image, it may be desirable to perform a few rounds of self-calibration \citepads[cf.]{2018arXiv180505266B} on the target field. This consists of extracting a model from the initial image and using it as a new calibration model, then re-imaging. Doing this will usually dramatically improve the final image. This now requires an understanding of interferometric calibration, which is the topic of the next chapter.

%\pg
%The framework for interferometric calibration is complex, and understanding it requires a good grasp on interferometry itself. For now, we will assume that calibration has been performed perfectly, and that the gain-corrections have been applied to the voltage measured by our antennas. We therefore work with the true signal from astrophysical sources until \cref{section.RIME}.

### 2018-11-12 source/Ch2-techniques/science.tex
asdasda

\pg
Of course, each individual galaxy will have differing contributions from different mechanisms - in practice, when studying galactic populations, the overall flux at a given frequency will simply be summed up for each galaxy and become one point in a Spectral Energy Distribution, or SED. However, when studying individual objects, it can be critical to understand which emission mechanism dominates at what frequencies. For example, the radio and far-infrared spectrum for nearby M82 are shown in Fig. \ref{plot.m82.spectrum}\footnote{Figure and work taken from the NRAO website. For further information, \href{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}{see here}}.
\begin{figure*}[!h]
\centering
\includegraphics[width=\textwidth]{images/M82Spectrum.png}
\caption{\label{plot.m82.spectrum} Radio and far-infrared spectrum for galaxy M82, as estimated \href{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}{by the NRAO online course} (\url{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}). The flat curve corresponds to free-free emission, while synchrotron radiation and thermal dust emission dominate at low and high frequencies respectively.}
\end{figure*}

>>>>

\pg
Of course, each individual galaxy will have differing contributions from different mechanisms - in practice, when studying galactic populations, the overall flux at a given frequency will simply be summed up for each galaxy and become one point in a Spectral Energy Distribution, or SED. However, when studying individual objects, it can be critical to understand which emission mechanism dominates at what frequencies. For example, the radio and far-infrared spectrum for nearby M82 are shown in Fig. \ref{plot.m82.spectrum}\footnote{Figure and work taken from the NRAO website. For further information, \href{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}{see here}}: \url{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}.
\begin{figure*}[!h]
\centering
\includegraphics[width=\textwidth]{images/M82Spectrum.png}
\caption{\label{plot.m82.spectrum} Radio and far-infrared spectrum for galaxy M82, as estimated \href{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}{by the NRAO online course} (\url{https://www.cv.nrao.edu/course/astr534/FreeFreeEmission.html}). The flat curve corresponds to free-free emission, while synchrotron radiation (negative slope) and thermal dust emission (postive slope) dominate at low and high frequencies respectively.}
\end{figure*}
